Ribosome accumulation during early phase resistance training

### 2020-09-12 manuscript.Rmd
misc updates

>>>>

# Figure legends

**Figure 1.** Study design (A) training load (B) and training outcomes (muscle strength, C; muscle thickness D).

**Figure 2.**  Total RNA and ribosomal RNA subspecies in response to trainin. Total RNA increased compared to non-training controls to post-training (12 sessions) and tended to normalize after de-training (A). There were no robust differences between different volume conditions in the training group (A). B shows primer locations targeting different ribosomal RNA subspecies. Subsets of ribosomal RNA showed robust increases compared to control 48 h after the first session and other after the training period (C). Error bars shows 95% CI. Asterisk in C indicates robust differences between volume conditions (a 95% CI of pairwise differences not containing 0).
